Online {\IterComp}\\Guided by Low Overhead Profiling

### 2017-09-01 cgo18mscr.tex
adds ToDo's

\begin{lstlisting}[caption={Post-processing of the CFG for populating all edge flows based on the collected probes.}, label={lst:populateEdgeFlows}, float]
// Inputs: CFG with the known edges flows from
//         the cotree (collected probes).
// Output: Updated CFG with all edge flows.
populateEdgeFlows(G) {
  changed = true
  while changed:
    changed = false
    for B in G.vertices():
      unIN = count( G.unknownIncomingEdges(B) )
      unOUT = count( G.unknownOutgoingEdges(B) )
      if unIN==0 and unOUT==1:
        //sum known incoming and outgoing edges
        sIN = sum( G.incomingEdges(B) )
        sOUT = sum( G.outgoingEdges(B) )
        //update unknown outgoing edge in B
        //with (sIN-sOUT)
        G.setUnknownOutgoingEdge(B, (sIN-sOUT))
        changed = true
      if unIN==1 and unOUT==0:
        //sum known incoming and outgoing edges
        sIN = sum( G.incomingEdges(B) )
        sOUT = sum( G.outgoingEdges(B) )
        //update unknown incoming edge in B
        //with (sOUT-sIN)
        G.setUnknownIncomingEdge(B, (sOUT-sIN))
        changed = true
}
\end{lstlisting}

@@

\begin{lstlisting}[caption={Pseudocode that describes how the edge information is used in order to extract the value that will be computed in a given instrumented basic block $B_I$. This algorithm could equally be implemented based on the predecessors.}, label={lst:instrValue}, float]
// Inputs: 1) CFG with the known edges flows
//            of the chords.
//         2) Basic block targeted for probing.
// Output: Work value to be incremented by the
//         given probe B.
instrValue(G, B, inc, dec) {
  value = 0
  for B in G.vertices():
    incB = set()
    decB = set()
    for succB in G.successor(B):
      incB = incB union inc[G.getEdge(B, succB)]
      decB = decB union dec[G.getEdge(B, succB)]
    if B in (incB - decB):
      value = value + w(B)
    if B in (decB - incB):
      value = value - w(B)
  return value
}
\end{lstlisting}

@@

>>>>

\begin{lstlisting}[caption={Post-processing of the CFG for populating all edge flows based on the collected probes.
\textbf{ToDo: Replace the algorithm with a formal data-flow equation.}}, label={lst:populateEdgeFlows}, float]
// Inputs: CFG with the known edges flows from
//         the cotree (collected probes).
// Output: Updated CFG with all edge flows.
populateEdgeFlows(G) {
  changed = true
  while changed:
    changed = false
    for B in G.vertices():
      unIN = count( G.unknownIncomingEdges(B) )
      unOUT = count( G.unknownOutgoingEdges(B) )
      if unIN==0 and unOUT==1:
        //sum known incoming and outgoing edges
        sIN = sum( G.incomingEdges(B) )
        sOUT = sum( G.outgoingEdges(B) )
        //update unknown outgoing edge in B
        //with (sIN-sOUT)
        G.setUnknownOutgoingEdge(B, (sIN-sOUT))
        changed = true
      if unIN==1 and unOUT==0:
        //sum known incoming and outgoing edges
        sIN = sum( G.incomingEdges(B) )
        sOUT = sum( G.outgoingEdges(B) )
        //update unknown incoming edge in B
        //with (sOUT-sIN)
        G.setUnknownIncomingEdge(B, (sOUT-sIN))
        changed = true
}
\end{lstlisting}

@@

\begin{lstlisting}[caption={Pseudocode that describes how the edge information is used in order to extract the value that will be computed in a given instrumented basic block $B_I$. This algorithm could equally be implemented based on the predecessors.
\textbf{ToDo: Using the vector format, we could replace this algorithm with a single equation. Let $V$ be the vector of $\{-1,0,1\}$ and $W$ the weight for each basic block.
This algorithm could be re-written as $reduce (+) (map (*) (zip V W))$.}
}, label={lst:instrValue}, float]
// Inputs: 1) CFG with the known edges flows
//            of the chords.
//         2) Basic block targeted for probing.
// Output: Work value to be incremented by the
//         given probe B.
instrValue(G, B, inc, dec) {
  value = 0
  for B in G.vertices():
    incB = set()
    decB = set()
    for succB in G.successor(B):
      incB = incB union inc[G.getEdge(B, succB)]
      decB = decB union dec[G.getEdge(B, succB)]
    if B in (incB - decB):
      value = value + w(B)
    if B in (decB - incB):
      value = value - w(B)
  return value
}
\end{lstlisting}

@@

\textbf{ToDo: Include results using Genetic Algorithm search.}
